ok. i shall not try to backdate entries for the end of november \amp december,
so here's what i remember of the last two weeks:
\begin{enumerate}
	\item \textit{documentation:} we all got together, made a poster, and
	wrote the report. this took\ldots\ longer than any of us would like to
	admit, but not so long as to be excessive.

	\item \textit{research:} i reread and re-described (in our report) a
	lot of the \arrl's existing work on \rf experimentation, with the
	intent to use it as technical and methodological inspiration for our
	own educational materials later.

	\item \textit{engineering:} evan and i discussed at length how exactly
	we're going to manage construction of 14 MHz circuitry effectively on
	perfboard, and at what stage we'd need to switch to transmission lines.
	the upshot was that we could persist on perfboard for quite a while
	(based on our other experiments at higher frequencies), but that
	antenna feedlines could be an issue.

	also: tested the phase-shifter again, tinkered with the tuning, etc. i
	think this one will really work, as it only has to be accurate across a
	narrow range of frequencies (which it is). next step is \dsp magic on
	the Teensy!
\end{enumerate}

speaking of: antennas for this project will be \emph{long!} we're operating in
the 20 meter band -- they'll be on the order of\ldots\ that long.

oh yeah, before i forget: since you'll probably have the entire project history
available to you, take a glance at the git log -- it probably includes other
stuff i forgot.
